%ACKNOWLEDGEMENTS page. 
%This page is optional

\clearpage
\begin{center}

\vspace*{5\baselineskip}
\textbf{\large Acknowledgements}
\end{center}

\hspace{10mm}I would like to thank those who contributed and supported through my graduate studies and research. First of all, I would like to express my sincere appreciation to
my advisor, Professor Kyle J. M. Bishop, for his guidance and support. I always think I am so lucky to have Kyle as my advisor. I am very grateful for your  patience, your guidance, your inspiring ideas and your academic insight  for the past five years, which make me not only a better researcher but also a better man. Kyle, you are one of the best teachers and mentors that I have learned so much from you on both research and life. I would also like to thank the members of my graduate
committee, Professor Oleg Gang, Professor Mijo Simunovic , and Professor Paul Chaikin, and Professor Sanat Kumar, all of whom have taught me through my graduate studies.

I thank to  all members of Bishop Group in the past and present who provide a nice environment in which to work as well as my friends who made my life in New York enjoyable. The
great friendships that I have made with them have given me things to look forwards to outside of
research as well as countless happy memories that I will always be thankful. I wish everyone in our group will have good research output and keep happy everyday. Thanks to Charles, Sabrina, Hae Ra,  Allan's mentoring during my first year. We have lots of good time during the experimental skills training sessions. I would also like to thank Yang, Wenjie and Shashank, whom I spend my most Ph.d time with. We moved together from State College to New York and helped each other on both research and life and I really hope I can spend more time you guys.  For Dimitri and Kiran, thank you for the invaluable discussion on data science and AI.Thank you for Zhengyan taking over this interesting research topic in the future.
% as well as being my audiences when I was talking stupid jokes. % I really hope you could find a girlfriend from southern China. 

Finally, I would like to express deep appreciation to my family for their support and love. I am sorry that I spend so much less time with you during my Ph.D study. I promise to be a better son, a better brother and a better husband. 
\clearpage

%\pagenumbering{gobble}  %remove page number on summary page
 

