\chapter{Colloidal robots: the end of the beginning }
\begin{center}
\textbf{Abstract}
\end{center}
This thesis started with introducing the motivation and background of colloidal robot. A fully autonomous colloidal robot should have a feedback system composed of actuators, sensors, and controllers.  In Chapter 2 and Chapter 3, we gave two examples on how to make actuators for colloidal robots with a high efficient electrostatics actuation mechanism called contact charge electrophoresis (CCEP). Chapter 2 showed the asymmetry of the colloid particle can provide a large design space for different kinds of actuation motions in colloidal robots.  Chapter 3 showed complex traveling actuation for colloidal robots can be achieved by coupling individual actuator's motion together.  In addition to actuation, we further proposed two strategies to design sensors and controllers for colloidal robots. With actively interacting the with environment through the feedback system, colloidal robots can finish some complex targets such as autonomous navigation. In Chapter 4, colloidal robots are designed to alter the shape versus the local information or stimulus. We programmed the shape and shape-shifting process versus different stimuli to let colloidal robots achieve global navigation with only local information. In Chapter 5, we programmed the external magnetic field used to actuate ferromagnetic colloidal robots. Such colloidal robots were also demonstrated to show navigation behaviors  (uphill or downhill) on an inclined slope. Though we have showed inspiring achievement with both experiment and computation efforts in this thesis, research pathway towards colloidal robot is just at the end of the beginning (or even not reach). Lots of more interesting and challenging problems still need to be solved related to colloidal robots field. The last chapter of this thesis is going to give an outlook for the future research direction of colloidal robots.
\section{Actuation Mechanism for  Colloids Robots}
 Lots of current actuation mechanisms have either very low energy conversion ($<0.1\%$) efficiency due to a large amount of heat dissipation or very slow speed, which is not compatible to the real living machines such as bacteria. Future development for  the actuation mechanism should focus on improving efficiency, speed, and robustness as well as understanding the detailed physics behind different mechanisms. Moreover, colloidal robots introduced in this thesis and lots of other papers have very limited degrees of freedom for their motions. Such motions are usually simply rolling, translating or turning around which is far from the various actuation mode in a robotic hand with many joints. New actuation mechanisms should also let colloidal robots have more degrees of freedom to move.  Another important characteristics of a good actuation mechanism  is flexible and robust. The actuation mechanism should work reliably for a large range of materials in different fluid environments. With respect to the robust characteristic,  the magnetic actuation mechanism stands out from other mechanisms. Because the magnetic force can be well controlled with less influences from the fluid environments or materials (as the example shown in chapter 5).

One interesting electrostatics actuation mechanism called Quincke rotation, which can generate fast autonomous rotation near the electrode with very low energy input is a promising new actuation mechanism \autocite{das2013electrohydrodynamic}. Different shapes such as spheres, ellipsoids and helix have shown high actuation speed in microscale\autocite{brosseau2019relating,das2019active}. A better understanding of dynamics in Quincke rotation can help us design faster and more efficient colloidal robots. However, the complex non-linear multipole electrodynamics and hydrodynamics problems in Quincke rotation are still unsolved, requiring  both experimental and theoretical study. More accurate  and  less time-consuming algorithm should be developed\autocite{fiore2019fast}.

Another research direction is developing a well packed autonomous platform to drive the motion of colloid  robots.  The autonomous platform should integrate the process in colloidal robots research from fabrication, observation to analysis and recycling. In an autonomous process, the platform can produce colloidal robots and insert colloidal robots into the experimental environment autonomously. Then the imaging process will be triggered  with feedback loop to actuate the microrobots. After observation, the colloidal robots should be collected by the platform for future implementations. A similar autonomous platform has been built to study chemical synthesis and biology research \autocite{grizou2020curious,chao2019systems}. The autonomous workflow platform can not only saving time during research but also accelerates the commercialized process of colloidal robots.   

\section{Swarm Colloidal Robots}
Swarm colloidal robots take advantage of the interactions among colloidal particles to generate high-level functions such as pattern formation and collective behaviors. In Chapter 3, we showed linear colloidal particle actuators can form travelling waves. An intuitive research direction is to explore 2 dimension electrostatic actuators' dynamics with the same system in Chapter 3. For the experiment, we can use two parallel plate electrodes and place actuators between the electrodes in a honeycomb or square lattice  holes to study the dynamics. The dynamics structures in 2D will be much more visually impressive than  1-d travelling waves. However,  there are some experimental technique challenges to put micron particles  inside micro honeycomb lattice holes. One possible solution is to use laser tweezers to place the micro particles into each hole one by one. Alternatively, we can also MEMS 's top-down fabrication to make the micro spheres in the micro holes with multiplayer's lithography, deposition, and etching. To model the system, it is very important to find a suitable coarse-grain model instead of direct detailed numerical simulations of all the particles. The coarse-grain model should be simple enough that doesn't require too much computational source, while it should be accurate enough to capture the key physics and  behaviors in the system similar to the model proposed in Chapter 3.

As we discussed in the first chapter, most of the swarm colloidal robots now are simply using passive interaction showing only one type of dynamics, which is not programmable. If the interactions between the colloidal particles can be re-programmed, a different mode of collective behaviors could be generated. Recent research has shown that the magnetic interactions between magnetic particles   can be programmed by introducing multi-pole interactions. These magnetic particles were programmed to show  different  equilibrium self-assembly structures subject to different interactions\autocite{niu2019magnetic}. Similar programmed method can be used in non-equilibrium swarm colloidal robots to generate different dynamics patterns. Moreover, collective behaviors among large amounts of micro scale colloidal particles  will generate impact in macro scale,  showing reconfigurable, adaptable and scalable  characteristics,  which is similar to  how the small living cells built the whole body. Thus, swarm colloidal robots can even provide revolutionary new actuation mechanism for the real size robotics. 
%%%%%%%%%
\section{Shape Shifting Colloids Robots}
To experimentally realize the autonomous navigation strategy with shape-shifting colloidal robots in Chapter 4, the key is to develop shape-shifting materials responding to the environmental stimulus. There several candidate materials such as  light response liquid crystal\autocite{palagi2016structured}, and thermal response shape memory alloy\autocite{busch1991shape}: liquid crystal can change the molecule's structure upon receiving photons from  light, leading to the shape shifting of liquid crystal; the atom lattice of shape memory alloy will change due to the thermal energy and will release back to normal in the room temperature. These materials have been reported working very well in microscale to form different structure subject stimulus\autocite{breger2015self}, although most papers use shape-shifting as a mechanism to actuate instead of sensing\autocite{tu2017self,li2018light}. A possible experiment system could use a dielectric (or magnetic nanoparticle embedded) light response liquid crystal materials with some designed shape.   The motion can be actuated via the outside electrostatic (or magnetic) field. With different environmental stimuli, the materials will change to different shapes simultaneously. The colloidal robots will continue the feedback loop of sensing and actuation, leading to navigation behaviors shown in Chapter 4. 

There several challenges to be solved for the experiment proposed above. The first challenge  is to design the shape shifting process for colloidal robots. We gave a simple example in Chapter 4 on how to design the shape-shifting process with the reverse design optimization. However, it will be hard to build a model perfectly predicting the motions of all different shape colloids in external field. Numerical models need to work together with large experiments efforts to help us fully understand how shape can direct different motions for colloidal robots\autocite{lee2019directed}. Then with a "dictionary" of shape and its corresponding motion, we can try to design the shape shifting process for colloidal robots based on the guideline in Chapter 4. The second challenge is to match the time scale between shape shifting rate and actuation speed. The changing rate of current shape shifting materials is relatively very low that will take seconds or even minutes to change one shape to another. When the colloidal robots sense a new environmental stimulus, it should change the shape simultaneously without too  much time delay. Late reaction time (or called as long memory) of shape-shifting materials will  lead to the wrong navigation direction of colloidal robots. Future research should focus on developing materials with fast-changing rate. The third challenge is to built a microscale stimulus landscape. The gradient of stimulus landscape should be small enough compared to the size of colloidal robots that colloidal robots only feel a uniform stimulus in one location. This requires a very precise  design of the micron scale topological structure such as micro patterned light grid to control the light intensity. 

Moreover, shape-shifting materials are working as only sensors. So if other internal states can change with the stimulus from the environments, these states can also be used as sensors for colloidal robots. For example, if the electric charge amount, some chemical species, the strength of magnetic dipole on the colloidal robots can change versus the environmental stimulus, all of these quantity can be used as sensors in a feedback loop to design the autonomous navigation strategy for colloidal robots.




\section{Programmable and Design the Colloids Robots}
For engineering applications and commercialized requirements, colloidal robots must be programmed and designed rationally, which is still a relatively blank research area. This is because most researchers in colloidal robots are from natural science fields like chemistry and physics. It is a pity that colloidal robots haven't arisen too much attention from researchers in robotics such as electrical engineers or computer scientists, who focus more on the programming and design problems\autocite{das2019cellular}.  The control strategy, design framework and program algorithm in large scale robots can help a lot in the research on colloidal robots.  Future research on colloidal robots should involve intensive collaborations between robotics field and colloid fields.

One very promising  direction is to use machine learning or artificial intelligent guiding the design of colloidal robots. There are lots of design parameters for a colloidal robot such as materials choice, shape's design, magnitude and form of the power source. The typical way for experimentalists is to do tons of repeating experiments either successful approaches or failed attempts during the research. The machine learning approach can make failure data more valuable. With clustering, classification and regression for the experimental data, machine learning (or deep learning) algorithm can not only find the pattern to design a good colloidal robot, but also be likely to find some nontrivial design rules for colloidal robots. In addition to studying large amounts of data with machine learning, optimization algorithm (or optimal design) can help us design colloidal robots with less time-consuming experiment approaches. If we know the design space for the colloidal robots, either with the experimental or simulation output, optimization algorithms (such as CME-ES algorithm in Chapter 4 can guide the selection of next design parameters in the design space. Also, recent reports showed Bayesian inference can help to estimate design parameters with fewer experiments \autocite{winslow2019characterization}.



Also, there are more functions beyond autonomous motion and navigation could be designed for colloidal robots. Cargo transportation is now an emerging research direction\autocite{demirors2018active,Martinez-Pedrero2015}. Basically, the colloidal robots can use physical interactions in the form of electrostatic, magnetic to hydrodynamics to attract and capture cargo. The colloidal robots will move cargo along some designed route and release the cargo in the destination via turning the interaction off. Future research could focus  on the developing method for cargo sorting and cargo assembling similar to Amazon robots in macro scale.


\section{Application of Colloidal Robots}
At the current stage, all of the colloidal robots' applications are still being explored in the lab. But with the unique properties of colloidal robots (cell scale size and different dynamics function), the potential applications for colloidal robots are very impressive. In the last section of this thesis, I will briefly discuss the applications for colloidal robots.

\textbf{Biomedical applications.} The biggest and most intuitive applications for the colloidal robots are medical applications. Colloidal robots are usually in the size of living cells so that they may work as "micro" surgery knives to remove tumors, transport drug or repair wound for patience. Several in vivo colloidal robotic experiments  on animals have been reported with promising results\autocite{Gao2015,li2018development}. There are several very strict standard must be satisfied when we design a colloidal robot for biomedical applications. First, the materials of colloidal robots must be biocompatible with no harm to the living system and have a pathway to be removed from the living body or alternatively can be digested by the living body without any side effects. The materials should also be modified to have proper chemical or physical affinity so that colloidal robots can carry drugs or attack the tumors in the living system. Some candidate materials are silica gel materials (PDMS) or some nontoxic metals. This requires tremendous in vivo experiments on animals before  any possible experiments on the human being. Second, the actuation mechanism for the colloidal robots must also be safe enough. For example, if we use a magnetic or electric field, the intensity of the external field shouldn't exceed the maximum bearing value of humans. These fields also shouldn't be  filtered or screened by some structures inside the human body. Therefore, magnetic field or acoustic field that have already by used in medical treatment are good  candidate actuation mechanisms.  Third, the cost of the whole colloidal robot's system should be kept as affordable as possible so that colloidal robots are tangible for most patients. Research on colloidal robots for biomedical applications must involve collaborations from doctors and scientists in medical school to get their insights and knowledge.

\textbf{Other applications.} Colloidal robots have been demonstrated with other interesting applications such as cleaning water, mixing fluid and lithography\autocite{soler2014catalytic,fei2019magneto,li2014nanomotor}. These applications all depend on the autonomous motion and navigation behaviors of colloidal robots. As a chemical engineer, I would like to propose an interesting application in the chemical engineering field: colloidal robots may be a new technology to enhanced oil recovery from the underground. In the petroleum industry, a large amount of crude oil (more than 50$\%$) is not extracted from rocks because they are in some dead-end micro pores with very low Reynolds number. Colloidal robots with autonomous motion and navigation behaviors can be designed with good crude oil affinity via chemical/physical modification. Then we can send these colloidal robots into the micro pore full of oil and collect the residual oil in micro poles.

As a short summary for the whole thesis, colloidal robots seem to be something from science fiction, but it is really happening now with many scientists and engineers from different fields working on it. We have some basics theoretical frameworks and some simple experimental demonstrations. The author has a very optimistic expectation for the future fast development of colloidal robots. Maybe in five or ten years, colloidal robots can be commercialized and serve people in different areas.  


